# Final plots in the manuscript

Necessary package:
```{r}
library(ggplot2)
```

## Figure in `fig:histone-history-1`

Reading the data:
```{r}
v1 = read.table("../cnn/csv/histone/v1.csv", header=TRUE, sep=",")
str(v1)

## add regularization type:
v1$method = "no-regularization"

v2 = read.table("../cnn/csv/histone/v2.csv", header=TRUE, sep=",")
str(v2)

## add regularization type:
v2$method = "L2-regularization"

## Append both datasets:
dat = rbind(v1,v2)
str(dat)
dat = within(dat, method<-factor(method,levels=c("no-regularization", "L2-regularization")))
```

Creating the plots:
```{r}
p1 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.6,0.8))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p1

pdf("two-conv2d-acc.pdf",height=4, width=8)
p1
dev.off()
```

```{r}
p2 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.45,0.85))+
  facet_wrap(~method)+
#  ggtitle("Loss")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p2

pdf("two-conv2d-loss.pdf",height=4, width=8)
p2
dev.off()
```

## Figure in `fig:histone-history-2`

Reading the data:
```{r}
v3 = read.table("../cnn/csv/histone/v3.csv", header=TRUE, sep=",")
str(v3)

## add regularization type:
v3$method = "no-regularization"

v4 = read.table("../cnn/csv/histone/v4.csv", header=TRUE, sep=",")
str(v4)

## add regularization type:
v4$method = "L2-regularization"

## Append both datasets:
dat = rbind(v3,v4)
str(dat)
dat = within(dat, method<-factor(method,levels=c("no-regularization", "L2-regularization")))
```

Creating the plots:
```{r}
p3 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.6,0.99))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p3

pdf("one-conv1d-two-conv2d-acc.pdf",height=4, width=8)
p3
dev.off()
```

```{r}
p4 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.05,1.45))+
  facet_wrap(~method)+
#  ggtitle("Loss")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p4

pdf("one-conv1d-two-conv2d-loss.pdf",height=4, width=8)
p4
dev.off()
```

## Figure in `fig:motif-discovery-history`

Reading the data:
```{r}
v1 = read.table("../cnn/csv/motif-discovery/v1.csv", header=TRUE, sep=",")
str(v1)

## add regularization type:
v1$method = "2 2D conv layers"

v2 = read.table("../cnn/csv/motif-discovery/v2.csv", header=TRUE, sep=",")
str(v2)

## add regularization type:
v2$method = "3 2D conv layers"

v3 = read.table("../cnn/csv/motif-discovery/v3.csv", header=TRUE, sep=",")
str(v3)

## add regularization type:
v3$method = "4 2D conv layers"


## Append both datasets:
dat = rbind(v1,v2,v3)
str(dat)
dat = within(dat, method<-factor(method))
```

Creating the plots:
```{r}
p5 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.5,0.8))+
  facet_wrap(~method)+
  xlab("")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p5

pdf("two-to-four-layers-acc.pdf",height=4, width=12)
p5
dev.off()
```

```{r}
p6 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.35,2.15))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_blank()
  )
p6

pdf("two-to-four-layers-loss.pdf",height=4, width=12)
p6
dev.off()
```

## Figure in `fig:motif-discovery-reg-history`

Reading the data:
```{r}
v3 = read.table("../cnn/csv/motif-discovery/v3.csv", header=TRUE, sep=",")
str(v3)

## add regularization type:
v3$method = "no-regularization"

v4 = read.table("../cnn/csv/motif-discovery/v4.csv", header=TRUE, sep=",")
str(v4)

## add regularization type:
v4$method = "L2-regularization"

## Append both datasets:
dat = rbind(v3,v4)
str(dat)
dat = within(dat, method<-factor(method,levels=c("no-regularization", "L2-regularization")))
```

Creating the plots:
```{r}
p7 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.45,0.8))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p7

pdf("four-layer-reg-acc.pdf",height=4, width=8)
p7
dev.off()
```

```{r}
p8 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.35,2.15))+
  facet_wrap(~method)+
#  ggtitle("Loss")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p8

pdf("four-layer-reg-loss.pdf",height=4, width=8)
p8
dev.off()
```

## Figure in `fig:deepram-history`

Reading data:
```{r}
emb.cnn = read.table("../cnn/csv/deepram/embedding/conv1d/v1.csv", header=TRUE, sep=",")
emb.cnn$model = "CNN"
emb.cnn$encoding = "embedding"

emb.cnnrnn = read.table("../cnn/csv/deepram/embedding/conv1d-recurrent/v1.csv", header=TRUE, sep=",")
emb.cnnrnn$model = "CNN-RNN"
emb.cnnrnn$encoding = "embedding"

emb.rnn = read.table("../cnn/csv/deepram/embedding/recurrent/v1.csv", header=TRUE, sep=",")
emb.rnn$model = "RNN"
emb.rnn$encoding = "embedding"

one.cnn = read.table("../cnn/csv/deepram/onehot/conv1d/v1.csv", header=TRUE, sep=",")
one.cnn$model = "CNN"
one.cnn$encoding = "one-hot"

one.cnnrnn = read.table("../cnn/csv/deepram/onehot/conv1d-recurrent/v1.csv", header=TRUE, sep=",")
one.cnnrnn$model = "CNN-RNN"
one.cnnrnn$encoding = "one-hot"

one.rnn = read.table("../cnn/csv/deepram/onehot/recurrent/v1.csv", header=TRUE, sep=",")
one.rnn$model = "RNN"
one.rnn$encoding = "one-hot"

## Appending data:
dat = rbind(emb.cnn, emb.cnnrnn, emb.rnn, one.cnn, one.cnnrnn, one.rnn)
str(dat)
dat = within(dat, model<-factor(model))
dat = within(dat, encoding <- factor(encoding))
```

Creating plots:
```{r}
p9 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.45,0.8))+
  facet_grid(encoding~model)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p9

pdf("cnn-rnn-acc.pdf",height=8, width=12)
p9
dev.off()
```

```{r}
p10 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.4,0.7))+
  facet_grid(encoding~model)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p10

pdf("cnn-rnn-loss.pdf",height=8, width=12)
p10
dev.off()
```

## Figure in `fig:cifar-10-comparison`

Reading in data:
```{r}
cifar = read.table("../cnn/csv/cifar-10/log.csv", header=TRUE, sep=",")
cifar$data = "CIFAR-10"
cifar$epoch = 0:39
str(cifar)
## keeping only the first 30 epochs
cifar2 = cifar[1:30,]
str(cifar2)

motif = read.table("../cnn/csv/motif-discovery/v3.csv", header=TRUE, sep=",")
motif$data = "motif-discovery"
str(motif)

## Append data:
dat = rbind(cifar2, motif)
dat = within(dat, data<-factor(data))
str(dat)
```

Creating the plots:
```{r}
p11 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.4,0.85))+
  facet_wrap(~data)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p11

pdf("cifar-10-comparison-acc.pdf",height=4, width=8)
p11
dev.off()
```

```{r}
p12 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.35,2.15))+
  facet_wrap(~data)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p12

pdf("cifar-10-comparison-loss.pdf",height=4, width=8)
p12
dev.off()
```

## Figure in `fig:optimizer`

Reading the data:
```{r}
adam = read.table("../nlp/UCI/baseline_uci_adam256_history.csv", header=TRUE, sep=",")
str(adam)
adam$epoch = adam$X
adam$optimizer = "Adam"

sgd = read.table("../nlp/UCI/baseline_uci_sgd256_history.csv", header=TRUE, sep=",")
str(sgd)
sgd$epoch = sgd$X
sgd$optimizer = "SGD"

## Appending the data:
dat = rbind(adam,sgd)
str(dat)
dat = within(dat, optimizer<-factor(optimizer))
```

Creating the plots:
```{r}
p13 = ggplot(dat, aes(x=epoch, y=accuracy))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.5,0.99))+
  facet_wrap(~optimizer, scales="free_x")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p13

pdf("baseline-uci-acc.pdf",height=4, width=8)
p13
dev.off()
```

```{r}
p14 = ggplot(dat, aes(x=epoch, y=loss))+geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.1,1.2))+
  facet_wrap(~optimizer, scales="free_x")+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p14

pdf("baseline-uci-loss.pdf",height=4, width=8)
p14
dev.off()
```

## Figure in `fig:splice-promoter-conv2d-history`

Reading the data:
```{r}
splice = read.table("../cnn/csv/splice-promoter/splice-conv2D.csv", header=TRUE, sep=",")
str(splice)

splice$method = "splice"

promoter = read.table("../cnn/csv/splice-promoter/promoter-conv2D.csv", header=TRUE, sep=",")
str(promoter)

promoter$method = "promoter"

## Append both datasets:
dat = rbind(splice,promoter)
dat = within(dat, method<-factor(method,levels=c("splice", "promoter")))
str(dat)
```

```{r}
p15 = ggplot(dat, aes(x=epoch, y=accuracy))+
  geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.45,1.0))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p15

pdf("simple-two-conv2d-acc.pdf",height=4, width=8)
p15
dev.off()
```

```{r}
p16 = ggplot(dat, aes(x=epoch, y=loss))+
  geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.0,0.72))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p16

pdf("simple-two-conv2d-loss.pdf",height=4, width=8)
p16
dev.off()
```

## Figure in `fig:splice-promoter-conv1d-history`

Reading the data:
```{r}
splice = read.table("../cnn/csv/splice-promoter/splice-conv1D.csv", header=TRUE, sep=",")
str(splice)

splice$method = "splice"

promoter = read.table("../cnn/csv/splice-promoter/promoter-conv1D.csv", header=TRUE, sep=",")
str(promoter)

promoter$method = "promoter"

## Append both datasets:
dat = rbind(splice,promoter)
dat = within(dat, method<-factor(method,levels=c("splice", "promoter")))
str(dat)
```

```{r}
p17 = ggplot(dat, aes(x=epoch, y=accuracy))+
  geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_accuracy),col="darkgreen", size=1.5)+
  ylim(c(0.375,1.0))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p17

pdf("simple-two-conv1d-acc.pdf",height=4, width=8)
p15
dev.off()
```

```{r}
p18 = ggplot(dat, aes(x=epoch, y=loss))+
  geom_line(col="blue4", size=1.5)+
  geom_line(aes(y=val_loss),col="darkgreen", size=1.5)+
  ylim(c(0.0,1.05))+
  facet_wrap(~method)+
     theme(
    plot.title = element_text(hjust=0.5, size=rel(1.6)),
    axis.title.x = element_text(size=rel(1.4)),
    axis.title.y = element_text(size=rel(1.4), angle=90, vjust=0.5, hjust=0.5),
    axis.text.x = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    axis.text.y = element_text(colour="grey", size=rel(1.2), angle=0, hjust=.5, vjust=.5, face="plain"),
    legend.text=element_text(size=rel(1.2)), legend.title=element_text(size=rel(1.5)),
    panel.background = element_blank(),
    axis.line = element_line(colour = "grey"),
    legend.position="none",
    strip.text = element_text(size = 17)
  )
p18

pdf("simple-two-conv1d-loss.pdf",height=4, width=8)
p18
dev.off()
```